\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-29 Paper/Paper.tex
finish abnormity models results draft

	Fig.~\ref{fig:gradCAM_multi_abnormity} demonstrates that the Abnormity Models may be able to correctly identify multiple abnormities on an image. Knowing that OCT and fundus images often do include more than one abnormity, we employ a method to determine the dominant abnormities. We input an image to the Abnormity Models and get the abnormity probabilities vector. If the abnormity with the highest probability has probability greater than 0.9, then we regard it as dominant; if not, we take the abnormity with the second high probability, and if the sum of the two probabilities is greater than 0.9, we regard them as codominant; we continue taking the abnormity with the next high probability until either the sum of probabilities reaches 0.9, or the number of abnormities reaches the maximum, which is 4.   050AO78.017\%, 152AF71.889\%

>>>>

	Fig.~\ref{fig:gradCAM_multi_abnormity} demonstrates that the Abnormity Models may be able to correctly identify multiple abnormities on an image. Knowing that OCT and fundus images often do include more than one abnormity, we employ a method to determine the codominant abnormities. We input an image to the Abnormity Models and get the abnormity probabilities vector. If the abnormity with the highest probability has probability greater than 0.9, it is regarded as dominant; if not, we continue taking the abnormity with the next high probability until either the sum of the probabilities of the chosen abnormities reaches 0.9, or the number of abnormities reaches the maximum, which is 4, and all the chosen abnormities are regarded as codominant.

	This codominant abnormities method allows the Abnormity Models to identify multiple abnormities. For example, the fundus image in Fig.~\ref{fig:gradCAM_multi_abnormity} only has ground truth label ``HE'', but the Fundus Model correctly predicts that it has codominant abnormities ``HE'' and ``HM''.
